\LARGE \bf Towards a Data-driven Approach to Motion Planning

### 2014-10-01 paper2015asml.tex
added the good trajectories

@@

>>>>

\newcommand{\gta}[3]{pictures/example_traj/Good/#1-snapshot-#3-#2}
\newcommand{\bta}[3]{pictures/example_traj/Bad/#1-snapshot-#3-#2}
\newcommand{\fta}[3]{pictures/example_features/#1\_#2\_#3}

@@

\begin{figure*}[t]
\begin{center}
\begin{tabular}{cccc}
\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_38_59}{3}{1}}
\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_38_59}{3}{2}}
\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_38_59}{3}{3}}
\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_38_59}{3}{4}}
\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_38_59}{3}{5}}\\

\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_39_22}{2}{1}}
\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_39_22}{2}{2}}
\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_39_22}{2}{3}}
\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_39_22}{2}{4}}
\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_39_22}{2}{5}}\\

\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_38_58}{3}{1}}
\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_38_58}{3}{2}}
\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_38_58}{3}{3}}
\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_38_58}{3}{4}}
\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_38_58}{3}{5}}\\

\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_39_36}{4}{1}}
\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_39_36}{4}{2}}
\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_39_36}{4}{3}}
\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_39_36}{4}{4}}
\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_39_36}{4}{5}}\\

\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_39_41}{2}{1}}
\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_39_41}{2}{2}}
\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_39_41}{2}{3}}
\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_39_41}{2}{4}}
\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_39_41}{2}{5}}\\

%\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_40_15}{2}{1}}
%\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_40_15}{2}{2}}
%\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_40_15}{2}{3}}
%\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_40_15}{2}{4}}
%\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_40_15}{2}{5}}\\

%\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_40_16}{3}{1}}
%\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_40_16}{3}{2}}
%\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_40_16}{3}{3}}
%\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_40_16}{3}{4}}
%\includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.19\textwidth]{\gta{2014_Sep_17_18_40_16}{3}{5}}\\

%bad trajs
%{2014_Sep_17_18_38_44}{1}
%{2014_Sep_17_18_39_17}{3}
%{2014_Sep_17_18_40_06}{1}
%{2014_Sep_17_18_40_21}{2}

\end{tabular}
\end{center}
\caption{Snapshots of favorably rated trajectories on all four categories by a large proportion of survey users}
\label{fig:good_traj}
\end{figure*}
